Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-09-02 draft.tex
fixed switched plots in results figure

\subsubsection{Size Groups}
%%
Many previously described results are confounded with subject size.
%%
Differences between male and female subjects are explained by to the average body size difference.
%%
For example, large subjects are already characterized by their rather straight spine.
%
The question is, whether the inter-group spine-variability parameter is enough for predicting other parameter or not.
%%
Dividing subjects into body size groups potentially highlights classifications not confounded by body size.
%%
\paragraph{Large Decision Trees. }
Back pain-associated variables can be explained for various size-groups, but we could not extract universal rules.
%%
Radiating back pain could be described with error rate of $0.39$ using 23 rules for subjects between $171-177~cm$ body size using \emph{torsion} and \emph{mean curvature}.
%%
For subjects sized $177-202~cm$ the accuracy drops to $0.47$ using 20  decision rules.
%%
There are several decision trees for laboratory values, such as alanine aminotransferase value (relevant for diagnosis of lover or gallbladder illness) in the blood can be described with a high precision of $0.4$ ($139-164~cm$) to $0.36$ ($164 - 171~cm$).
%%
Similar values can be observed for cholesterol or age.
%%
Due to the large decision trees, these results are not usable and impose overfitting to the data.
%%
\paragraph{Small Decision Trees. }
%%
The dummy variables show several variables described using only one decision rule with accuracy between $0,42$ to $0,47$.
%%
Most of these variables have a dominant manifestation and the classifier shows a low detection precision for the second manifestation.
%%
These variables include nutrition parameter, thyroid disorder and social problems induced by back pain.

>>>>

\subsubsection{Size Groups}
%%
Many previously described results are confounded with subject size.
%%
Differences between male and female subjects are explained by to the average body size difference.
%%
For example, large subjects are already characterized by their rather straight spine.
%
The question is, whether the inter-group spine-variability parameter is enough for predicting other parameter or not.
%%
Dividing subjects into body size groups potentially highlights classifications not confounded by body size.
%%
\paragraph{Large Decision Trees. }
Back pain-associated variables can be explained for various size-groups, but we could not extract universal rules.
%%
Radiating back pain could be described with error rate of $0.39$ using 23 rules for subjects between $171-177~cm$ body size using \emph{torsion} and \emph{mean curvature}.
%%
For subjects sized $177-202~cm$ the accuracy drops to $0.47$ using 20  decision rules.
%%
There are several decision trees for laboratory values, such as alanine aminotransferase value (relevant for diagnosis of lover or gallbladder illness) in the blood can be described with an error rate of $0.4$ ($139-164~cm$) to $0.36$ ($164 - 171~cm$).
%%
Similar values can be observed for cholesterol or age.
%%
Due to the large decision trees, these results are not usable and impose overfitting to the data.
%%
\paragraph{Small Decision Trees. }
%%
The dummy variables show several variables described using only one decision rule with accuracy between $0,42$ to $0,47$.
%%
Most of these variables have a dominant manifestation and the classifier shows a low detection precision for the second manifestation.
%%
These variables include nutrition parameter, thyroid disorder and social problems induced by back pain.
